### 2022-07-27 paper/localpsf.tex
minor change to make sure it reads f^{n_k} in the radial basis function interpolation section

Interpolation is performed using the following radial basis function scheme:
\begin{equation}
\Aker(y,x) \approx \widetilde{\Aker}(y,x) := \sum_{i=1}^{\numnbr} \rbfweight_i~ \rbf\left(\|x-x_i\|\right),
\end{equation}
where $\rbfweight_i$ are weights, and $\rbf$ is a polyharmonic spline radial basis function, which is defined as follows:
\begin{equation}
\rbf(r) := \begin{cases}
r^\gdim, & \gdim=1,3,5,\dots \\
r^\gdim \log r, & \gdim=2,4,6,\dots
\end{cases}
\end{equation}
for $r>0$, and $\rbf(0):=0$. The vector of weights, $\rbfweight = (\rbfweight_1, \rbfweight_2, \dots, \rbfweight_{\numnbr})^T$, is found as the solution to the $\numnbr \times \numnbr$ linear system
\begin{equation}
B \rbfweight = f,
\end{equation}
where $B \in \mathbb{R}^{\numnbr \times \numnbr}$ has entries
$
B_{ij} := \rbf\left(\|x_i - x_j\|\right),
$
and $f \in \mathbb{R}^\numnbr$ has entries $f_i$ from \eqref{eq:fxyxp}. Polyharmonic spline radial basis function interpolation yields the smoothest interpolant of the given points and values, in a certain least-squares sense \cite{Duchon77}. For more details on radial basis function interpolation, see \cite{Wendland04}. 
%The interpolation procedure is illustrate in Figure \ref{fig:rbf_interpolation}.

>>>>

Interpolation is performed using the following radial basis function scheme:
\begin{equation}
\Aker(y,x) \approx \widetilde{\Aker}(y,x) := \sum_{i=1}^{\numnbr} \rbfweight_i~ \rbf\left(\|x-x_i\|\right),
\end{equation}
where $\rbfweight_i$ are weights, and $\rbf$ is a polyharmonic spline radial basis function, which is defined as follows:
\begin{equation}
\rbf(r) := \begin{cases}
r^\gdim, & \gdim=1,3,5,\dots \\
r^\gdim \log r, & \gdim=2,4,6,\dots
\end{cases}
\end{equation}
for $r>0$, and $\rbf(0):=0$. The vector of weights, $\rbfweight = (\rbfweight_1, \rbfweight_2, \dots, \rbfweight_{\numnbr})^T$, is found as the solution to the $\numnbr \times \numnbr$ linear system
\begin{equation}
B \rbfweight = f,
\end{equation}
where $B \in \mathbb{R}^{\numnbr \times \numnbr}$ has entries
$
B_{ij} := \rbf\left(\|x_i - x_j\|\right),
$
and $f \in \mathbb{R}^{\numnbr}$ has entries $f_i$ from \eqref{eq:fxyxp}. Polyharmonic spline radial basis function interpolation yields the smoothest interpolant of the given points and values, in a certain least-squares sense \cite{Duchon77}. For more details on radial basis function interpolation, see \cite{Wendland04}. 
%The interpolation procedure is illustrate in Figure \ref{fig:rbf_interpolation}.
